Comprehensive Quality-Aware Automated Semantic Web Service Composition

### 2017-01-25 paper.tex
up

\title{Comprehensive Quality-Aware Automated Semantic Web Service Composition}
\author{\IEEEauthorblockN{Michael Shell}
\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
Georgia Institute of Technology\\
Atlanta, Georgia 30332--0250\\
Email: http://www.michaelshell.org/contact.html}
\and
\IEEEauthorblockN{Homer Simpson}
\IEEEauthorblockA{Twentieth Century Fox\\
Springfield, USA\\
Email: homer@thesimpsons.com}
\and
\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
\IEEEauthorblockA{Starfleet Academy\\
San Francisco, California 96678--2391\\
Telephone: (800) 555--1212\\
Fax: (888) 555--1212}}
\makeatletter
%\usepackage[pdfauthor={\@author}, pdftitle={\@title}]{hyperref}
%\makeatother

%\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}}

\begin{document}

\maketitle
\vspace{-0.8cm}

\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major governance challenges faced by researchers (semantic matching and QoS optimisation). Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning. QoS optimisation aims to meet non-functional requirement of service users. e.g minimum cost, maximal reliability. Many scholars have looked into nonfunctional optimisation problems in QoS-aware web service composition applying AI planning and Evolution Computing techniques. To meet users' requirement, one often needs to consider both semantic matching and QoS optimisation simultaneously. Existing works on web service composition often concerns either semantic service composition or QoS-aware service composition. However, there are very few works concerns both quality of semantic matchmaking and quality of services at the same time. Therefore, In this paper we consider two quality dimensions in a proposed more applicable comprehensive quality model for semantic web service composition, and present a automated semantic web service composition approach that can generate service composition solutions that meet both functional and non-functional requirement. We will evaluate our approach utilising a semantic benchmark dataset.

@@

\begin{table}[]
\centering
\caption{Mean time results for comparing GP-based approach}
\label{meanTime}
\begin{tabular}{l|l|l}
\hline
\multicolumn{1}{c|}{Dataset} & PSO-based approach & GP-based approach  \\ \hline
WSC09 01                     &12907.533333 $\pm$ 8105.111787      &5168.166667 $\pm$ 520.475319 $\downarrow$                \\ \hline
WSC09 02                     &292346.400000 $\pm$  96726.846023 $\uparrow$   &27483.100000 $\pm$  3083.391833           \\ \hline
WSC09 03                     & 12907.533333 $\pm$ 8105.111787 $\pm$ $\uparrow$  &28053.166667 $\pm$ 3202.059629            \\ \hline
WSC09 04                     & 6553640.033333 $\pm$ 1468203.652702 $\pm$ $\uparrow$  &540418.366667 $\pm$ 186540.432797            \\ \hline
WSC09 05                     & 1208192.500000 $\pm$ 266911.585694 $\pm$ $\uparrow$  &180408.366667 $\pm$ 435246.958095            \\ \hline
\end{tabular}
\end{table}

>>>>

\title{Comprehensive Quality-Aware Automated Semantic Web Service Composition}
 \author{Chen Wang, Hui Ma, Aaron Chen\\ School of
 Engineering and Computer Science, Victoria University of Wellington, New Zealand\\
Email: chen.wang@ecs.vuw.ac.nz, hui.ma@ecs.vuw.ac.nz, aaron.chen@ecs.vuw.ac.nz}

\usepackage[pdfauthor={\@author}, pdftitle={\@title}]{hyperref}
\makeatother

%\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}}
\vspace{-1.5cm}

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major governance challenges faced by researchers (semantic matching and QoS optimisation). Semantic matchmaking aims to discover interoperable web services that can interact with each other to provide rich functionalities through language understanding and reasoning. QoS optimisation aims to meet non-functional requirement of service users. e.g minimum cost, maximal reliability. Many scholars have looked into nonfunctional optimisation problems in QoS-aware web service composition applying AI planning and Evolution Computing techniques. To meet users' requirement, one often needs to consider both semantic matching and QoS optimisation simultaneously. Existing works on web service composition often concerns either semantic service composition or QoS-aware service composition. However, there are very few works concerns both quality of semantic matchmaking and quality of services at the same time. Therefore, In this paper we consider two quality dimensions in a proposed more applicable comprehensive quality model for semantic web service composition, and present a automated semantic web service composition approach that can generate service composition solutions that meet both functional and non-functional requirement. We will evaluate our approach utilising a semantic benchmark dataset.

@@

\begin{table}[]
\centering
\caption{Mean time results for comparing GP-based approach}
\label{meanTime}
\begin{tabular}{l|l|l}
\hline
\multicolumn{1}{c|}{Dataset} & PSO-based approach & GP-based approach  \\ \hline
WSC09 01                     &12907 $\pm$ 8105      &5168 $\pm$ 520 $\downarrow$                \\ \hline
WSC09 02                     &292346 $\pm$  96727    &27483 $\pm$  3083 $\downarrow$          \\ \hline
WSC09 03                     & 12908 $\pm$ 8105   &28053 $\pm$ 3202 $\downarrow$           \\ \hline
WSC09 04                     & 6553640 $\pm$ 1468204   &540418 $\pm$ 186540 $\downarrow$            \\ \hline
WSC09 05                     & 1208193 $\pm$ 266916   &180408 $\pm$ 435247 $\downarrow$           \\ \hline
\end{tabular}
\end{table}
